Constant-sized correlations are sufficient for robust self-testing of maximally entangled states with unbounded dimension

### 2019-05-03 Draft/draft.tex
Honghao: edits of section 1

\begin{abstract}
	We show that for any prime odd integer $d$ with primitive $r$, there exists a correlation of size
	$\Theta(r^2)$ that can robustly self-test a maximally entangled state of dimension $4d-4$. Our result is
	inspired by the robust self-testing result by Bamps and Pironio (\textit{Physical Review A} $91.5$ $(2015)$) and
	techniques introduced by Slofstra (\textit{Forum of Mathematics, Pi}. Vol. $7$, $2019$). Since there are
	infinitely many prime numbers with primitive root at most $5$ (\textit{The Mathematical Intelligencer} $10.4$ ($1988$)), 
	our result implies that constant-sized correlations are sufficient for robust self-testing of maximally entangled states
	with unbounded local dimension.
\end{abstract}
%========================================
\section{Introduction}
\label{sec:intro}
%========================================
Self-testing is a unique phenomenon of quantum mechanics. It has many applications in quantum
delegated computation \cite{ruv2013,cgsv2017} and device independent quantum cryptography
\cite{qkd2011,qkd2014,miller2016,fu2018,eat2018}.

The case of self-testing $2$-dimensional EPR pair is fully understood. One can robustly self-test
one copy of it by the CHSH inequality \cite{bamps2015}. and self-test many copies of the $2$-dimensional EPR
pair in parallel \cite{mckague2016, coladan2017parallel}. 
Self-testing general $d$-dimensional EPR pairs is a harder task.
Proving robustness is harder.

>>>>

\begin{abstract}
	We show that for any prime odd integer $d$ with primitive $r$, there exists a correlation of size
	$\Theta(r^2)$ that can robustly self-test a maximally entangled state of dimension $4d-4$. Our result is
	inspired by the robust self-testing result by Bamps and Pironio (\textit{Physical Review A} $91.5$ $(2015)$) and
	techniques introduced by Slofstra (\textit{Forum of Mathematics, Pi}. Vol. $7$, $2019$). Since there are
	infinitely many prime numbers with primitive root at most $5$ (\textit{The Mathematical Intelligencer} $10.4$ ($1988$)), 
	our result implies that constant-sized correlations are sufficient for robust self-testing of maximally entangled states
	with unbounded local dimension.
\end{abstract}
%========================================
\section{Introduction}
\label{sec:intro}
%========================================
Self-testing is a unique phenomenon of quantum mechanics. It has many applications in quantum
delegated computation \cite{ruv2013,coladan2017verifier} and device independent quantum cryptography
\cite{miller2017,fu2018,eat2018}.
\hfc{Which DIQKD paper should I cite?}

The case of self-testing $2$-dimensional EPR pair is fully understood. One can robustly self-test
one copy of it by the CHSH inequality \cite{bamps2015}. and self-test many copies of the $2$-dimensional EPR
pair in parallel \cite{mckague2016, coladan2016parallel, lowdegree}. 
Self-testing general $d$-dimensional EPR pairs is a harder task.
Coladangelo, Goh and Scarani has shown that all pure bipartite entangled states can be self-tested \cite{coladan2017all}
by constructing an explicit correlation of size $\Theta(d^2)$ that can be used for self-testing,
which is the only result about the general $d$-dimensional case so far.
However, proving the robustness of the correlation remains an open problem. 
Without robustness, we cannot infer anything about a quantum strategy if
the produced correlation deviates from the ideal correlation, no matter how small the 
deviation is.
